Linking hypothesis and number of response options modulate inferred scalar implicature rate

### 2018-12-17 manuscript.tex
added paragraph on data analysis

>>>>

\change{As suggested above, the quantitative predictions of our model will depend crucially on the values assigned to its free parameters - including (but not limited to) the probability thresholds and speaker costs of possible utterances. However, the values of these parameters can be estimated in a principled and informed manner through Bayesian statistical analysis of our experimental data. Samples from prior distributions over possible parameter values yield predicted patterns of response, which are then compared against empirically-observed response patterns in order to determine the a posteriori probability that these values are in fact the 'real' latent parameter values. The resulting posterior distributions are sampled from in turn, in order to parameterize the model and assess overall quantitative fit given the data. Though we leave a quantitative assessment of our model to future work (Waldon et al., in prep), we sketch the general procedure here to emphasize that the model is amenable to rigorous and data-driven evaluation.}
